Data Processing

### 2024-04-08 analysis/documents/1-data-preparation.qmd
add Ontario map

cams_sf_coords <- dplyr::bind_cols(cams_sf, coords)

@@

```{r eval=do_eval}
#| label: process-zones

zones_filtered <- 
  sf::st_read(here::here("data-raw","spatial", "ecozones", "EcoZone" ,"EcoZone.shp"),
              quiet = TRUE) |> 
  sf::st_transform(crs = sf::st_crs(cams_sf)) |>
  sf::st_filter(cams_sf_coords)

@@

saveRDS(base, here::here("data", "objects", "base_map.rds"))
```

>>>>

cams_sf_coords <- dplyr::bind_cols(cams_sf, coords) |>
  dplyr::mutate(
    month_year_deployed = paste(lubridate::month(date_deployed, label = T, abbr = T), 
                                lubridate::year(date_deployed)), 
    month_year_retrieved = paste(lubridate::month(date_retrieved, label = T, abbr = T), 
                                 lubridate::year(date_retrieved)), 
    deployment_group = paste0(month_year_deployed, ifelse(
      month_year_retrieved == "NA NA", "", paste(" -", month_year_retrieved))))

@@

```{r eval=do_eval}
#| label: process-zones
zones <- sf::st_read(here::here("data-raw","spatial", "ecozones", "EcoZone" ,"EcoZone.shp"),
              quiet = TRUE) |> 
  sf::st_transform(crs = sf::st_crs(cams_sf))
zones_filtered <- zones |>
  sf::st_filter(cams_sf_coords)

@@

saveRDS(base, here::here("data", "objects", "base_map.rds"))

ont_map <- ggmap::get_stadiamap(bbox = c(left = as.numeric(sf::st_bbox(zones)[1])-1, 
                                         bottom = as.numeric(sf::st_bbox(zones)[2])+1, 
                                         right = as.numeric(sf::st_bbox(zones)[3])-1,
                                         top = as.numeric(sf::st_bbox(zones)[4])+1), 
                            zoom = 5, maptype = "stamen_terrain")

ont_base <- ggmap::ggmap(ont_map) +
  ggplot2::labs(x = "Longitude", y = "Latitude") +
  ggplot2::geom_path(data = pols, ggplot2::aes(x = X, y = Y), col = 1, linewidth = 0.2) +
  ggplot2::geom_rect(
    xmin = -90,
    ymin = 50,
    xmax = -83,
    ymax = 55.5,
    fill = NA, 
    colour = "black",
    size = 0.6
  )

saveRDS(ont_base, here::here("data", "objects", "ont_base_map.rds"))
```
